---
title: "Diversity, integration, and variability of intergenerational relationships in old age: new insights from personal network research"
description: |
  Reproducible project
author:
  - name: Raffaele Vacca
    url: http://www.raffaelevacca.com/
    affiliation: Department of Social and Political Sciences, University of Milan
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    number_sections: false
    toc_float: true
---

**Reproducible project for:** 

Vacca, R., & Bianchi, F. (2024). Diversity, integration, and variability of intergenerational relationships in old age: new insights from personal network research.

**Index:**

`./`

* `Vacca_Bianchi_2024_SSR.Rmd`: knit all scripts together.
* `Vacca_Bianchi_2024_SSR.html`: all output.

`scripts/`

* `setup.R`: set project packages, objects, functions.
* `data.R`: create, recode, clean variables.
* `models.R`: fit statistical models.
* `fig_x.R` and `tab_x.R`: create each figure and table.

```{r, include = FALSE}
# Set global options
knitr::opts_chunk$set(echo = FALSE)
```


```{r, include = FALSE}
# Setup: project packages, functions, objects
source("./scripts/setup.R",
       local = knitr::knit_global()
       )
```

```{r, include = FALSE}
# Data construction
source("./scripts/data.R",
       local = knitr::knit_global()
       )
```

```{r, cache = TRUE, cache.extra = tools::md5sum("./scripts/models.R")}
# Ego-level and multilevel regression models
source("./scripts/models.R",
       local = knitr::knit_global()
       )
```


# Table 1

```{r, warning = FALSE, results='asis'}
source("./scripts/tab_1.R",
       local = knitr::knit_global()
       )
```

# Table 2

```{r, warning = FALSE, results='asis'}
source("./scripts/tab_2.R",
       local = knitr::knit_global()
       )
```

# Figure 1

```{r, warning = FALSE}
source("./scripts/fig_1.R",
       local = knitr::knit_global()
       )
```

# Figure 2

```{r, warning = FALSE, fig.height=5.5, fig.width=5}
source("./scripts/fig_2.R",
       local = knitr::knit_global()
       )

print(p)
```

# Figure 3

```{r, warning = FALSE, fig.width = 8, fig.height= 10.5}
source("./scripts/fig_3.R",
       local = knitr::knit_global()
       )

print(p)
```

# Figure 4

```{r, warning = FALSE, fig.height=8, fig.width=10}
source("./scripts/fig_4.R",
       local = knitr::knit_global()
       )

print(p)
```

# Table S1

Done manually (no code).

# Table S2

```{r, warning = FALSE, results='asis'}
source("./scripts/tab_S2.R",
       local = knitr::knit_global()
       )
```

# Table S3

```{r, results="asis"}
source("./scripts/tab_S3.R",
       local = knitr::knit_global()
       )
```

# Table S4

```{r, results="asis"}
source("./scripts/tab_S4.R",
       local = knitr::knit_global()
       )
```

# Table S5

```{r, results="asis"}
source("./scripts/tab_S5.R",
       local = knitr::knit_global()
       )
```

# Table S6

```{r, warning = FALSE, results='asis'}
source("./scripts/tab_S6.R",
       local = knitr::knit_global()
       )
```

# Table S7

```{r, warning = FALSE, results='asis'}
source("./scripts/tab_S7.R",
       local = knitr::knit_global()
       )
```

# Figure S1

```{r, warning = FALSE, fig.height=7, fig.width=12}
source("./scripts/fig_S1.R",
       local = knitr::knit_global()
       )

print(p)
```

# Figure S2

```{r, warning = FALSE, fig.width = 8, fig.height= 10.5}
source("./scripts/fig_S2.R",
       local = knitr::knit_global()
       )

print(p)
```

# Figure S3

```{r, warning = FALSE, fig.height=8, fig.width=10}
source("./scripts/fig_S3.R",
       local = knitr::knit_global()
       )

print(p)
```

# Session info

```{r, echo = FALSE}
session_info(pkgs = "attached")
```

